---
output: 
  html_document:
    code_folding: hide
---

# **Include library**
```{r}
library(ggplot2)
```

# **Read data**
```{r}
data <- read.csv('data.csv')
summary(data)
```

# **Histogram of price**
```{r}
hist(data$price, main = 'Price', breaks = 200)
```

# **Histogram of price in specific range 0 - 5,000,000**
```{r}
hist(data$price, main = 'Price', breaks = 200, xlim = c(0, 5e6))
```

# **Histogram of sqft_living**
```{r}
hist(data$sqft_living, main = 'Square feet of living room', breaks = 200)
```

# **Histogram of sqft_lot**
```{r}
hist(data$sqft_lot, main = 'Square feet of lot', breaks = 200)
```

# **Histogram of sqft_above**
```{r}
hist(data$sqft_above, main = 'Square feet of above floor', breaks = 200)
```

# **Histogram of sqft_basement**
```{r}
hist(data$sqft_basement, main = 'Square feet of basement', breaks = 200)
```

# **Histogram of yr_built**
```{r}
hist(data$yr_built, main = 'Year built', breaks = 200)
```

# **Boxplot of Price by City**
```{r}
pl <- qplot(data = data, x = city, y = price, main = 'House price by city', size = I(0.5), shape = I(15))
pl + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# **Boxplot of Year Built by City**
```{r}
pl2 <- qplot(data = data, x = city, y = yr_built, main = 'Year built by city', size = I(0.5), shape = I(15))
pl2 + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# **Scatterplot of Price and sqft_living, where price is in 0 - 2,500,000 and sqft_living is in 0 - 5,000**
```{r}
qplot(data = data, x = sqft_living, y = price, size = I(0.5), shape = I(15), main = 'Scatter plot of Price and square feet of living room', ylim = c(0, 2.5e6), xlim = c(0, 5000))
```

# **Linear regression, regression price by sqft_living, considering only price in 0 - 2,500,000 and sqft_living in 0 - 5,000**
```{r}
filtered_data = data[(data$price <= 2.5e6) & (data$sqft_living <= 5000),]
price = filtered_data$price
sqft_living = filtered_data$sqft_living
plot(sqft_living, price)
model <- lm(price ~ sqft_living)
points(sqft_living, model$coefficients[1] + model$coefficients[2] * sqft_living, type = 'l', col = 4)
```